\documentclass{article}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{titlesec}

% ====================================== %
\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    top=1mm,
    bottom=1mm,
}

\titlespacing*{\section}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}
% ====================================== %

\title{TEPS Notes}
\author{@sonnyzxc}
\date{May 2025}

\begin{document}
\maketitle

\section*{Voacabulary}
\begin{multicols}{2}
\begin{description}
    \item[Aberrant] departing from an accepted standard.
    \item[Abnegate] renounce of reject (something desirable or valueable).
    \item[Amicable] (of relations between people) having a spirit of friendliness; without serious disagreement or rancor.
    \item[Amity] a friendly relationship.
    \item[Assiduous] showing great care and perseverance.
    \item[Barren] (of land) too poor to produce much or any vegetation.
    \item[Brawny] physically strong.
    \item[Collocations] the combination of words formed when two or more words are often used together (e.g. strong coffee, heavy drinker).
    \item[Decrepit] worn out or ruined because of age or neglect.
    \item[Despondent] in low spirits from loss of hope or courage.
    \item[Ennui] a feeling of listlessness and dissatisfaction arising from a lack of occupation or excitement.
    \item[Extricate] free (someone or something) from a constraint or difficulty.
    \item[Feckless] useless.
    \item[Foray] a short visit, especially with a known purpose.
    \item[Fractious] difficult to control.
    \item[Impiety] lack of piety or reverence.
    \item[Innocuous] not harmful or offensive.
    \item[Inscrutable] impossible to understand or interpret.
    \item[Inundated] overwhelm (someone) with things or people to be dealt with; flood.
    \item[Irascible] having or showing a tendancy to be easily angered.
    \item[Lauded] highly praised or admired.
    \item[Mar] impair the appearance of; disfigure.
    \item[Prerogrative] a right or privilege exclusive to a particular individual or class.
    \item[Prosaic] unromantic; dull; dry.
    \item[Prudent] wise.
    \item[Sagacious] having or showing keen mental discernment and good judegment.
    \item[Stupendous] extremeley impressive.
    \item[Upbraid] find fault with (someone); scold.
    \item[Vacuous] having or showing a lack of thought or intelligence; mindless.
    \item[Vanity] excessive pride in or admiration of one's own appearance; quality of being worthless.
    \item[Vapid] offering nothing that is stimulating or challenging.
    \item[Verve] vigour and enthusiasm.
\end{description}
\end{multicols}


\section*{Past Paper Scores}
\begin{tabularx}{\textwidth}{c c c c c c l}
\toprule
\textbf{Test} & \textbf{청해 (/40)} & \textbf{어휘 (/30)} & \textbf{문법 (/30)} & \textbf{독해 (/35)} & \textbf{Total (/135)} & \textbf{Date} \\
\midrule
1 & 38 & 28 & 26 & 33 & 125 & 1st March 2025 \\
2 & 39 & 28 & 28 & 34 & 129 & 2nd March 2025 \\
3 & 39 & 29 & 28 & 35 & 131 & 4th March 2025 \\
4 & 39 & 29 & 28 & 34 & 130 & 6th March 2025 \\
5 & 40 & 28 & 28 & 33 & 129 & 7th March 2025 \\
\bottomrule
\end{tabularx}

\end{document}
